NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-08-31 Manuscript/manuscriptPS.tex
Add discussion about hydration levels in simulations and experiments

@@

\todo{Should we discuss about hydration levels in experiments and simulations?}

>>>>

In the experiment from the literature used in this work~\cite{browning80,roux90},
the lipids were first soluted to the buffer and then centrifuged to a pellet which
was used in the measurements. In such experiments the samples contain approximately
10~wt~\% of lipids~\cite{browning80,roux88,roux90}, which is less than in
gravimetric experiments (60~wt~\%) and simulations (approx. 50-60~wt~\%) in this work.
Since multilamellar structures of pure PS lipids swell due to the electrostatic repulsion,
the larger repeat distances are expected in samples with lower lipid concentrations~\cite{millman82}.
However, the PS headgroup order parameters from gravimetric sample are in good agreement
with centrifuged sample (Fig. \ref{HGorderParameters}) and the equlibrium repeat distance decreases
already above 500~mM concentration of monovalent ions close to the simulation box sizes \cite{millman82,rand89}.
Therefore, the hydration levels of multilamellae are expected to be sufficiently similar
in simulations and the reference experiments.

@@
